plots for paper

### 2019-10-02 src/plots for paper.Rmd
still hate R...

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)

@@

```{r}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

binprob <- function(x){
    ifelse(x > 0 & x <0.4, 1,
    ifelse(x <= 0, 0, NA))
}

for (m in 1:length(mthord)){
  mth <- "dec"
  clogasc_list <- list.files(paste0("../output/maxent/predictions/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- raster::mask(x = cumasc, mask = outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_binned_avgprob_", ascname, ".asc"), overwrite = TRUE)
    #plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_binned_avgprob_", ascname, ".png")), overwrite = TRUE)
    #dev.off() # stops automatic saving of the plot to a png
  }
}
```

get data to plot probability by depth... 
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_u0.4_binned_avgprob_", ".*asc"), full.names = TRUE)

  for (lyr in 1:nlayers(binaryavgstack)){
    ascname <-  str_sub(ascdepth[lyr], 63, -5)
    dlay <- binaryavgstack[[lyr]]
    lyrsum <- cellStats(dlay, sum)
    stackstathigh$prob_bin[lyr] <- lyrsum
    stackstathigh$asclayer[lyr] <- ascname

  }
  write.csv(stackstathigh, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_probbin_cellcount_bydepth_avg.csv"), row.names = FALSE)
}

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  probblst <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_u0.4_probbin_cellcount_bydepth_avg.csv"), full.names = TRUE)
  stackstat <- read.csv(probblst[1])

  colnames(stackstat) <- c("depth", "0 - 0.39")
  stackstat <- melt(stackstat, id = "depth")
  stackstat <- stackstat[!(stackstat$depth == "1151.99"), ]
  stackstat <- stackstat[!(stackstat$depth == "1265.86"), ]
  stackstat <- stackstat[!(stackstat$depth == "1387.38"), ]

  write.csv(stackstat, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_allprobbin_cellcount_bydepth_avg.csv"), row.names = FALSE)
}

get proportions...

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)

for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_allprobbin_cellcount_bydepth_avg.csv"), header = TRUE, stringsAsFactors=FALSE)
  for (r in 1:nrow(a)){
    a$Depth[r] <- gsub("prob_avg_cloglog_", "", x = a$Depth[r])
    d1 <- str_sub(a$Depth[r], end = 4)
	  for (ro in 1:nrow(cumst1)){
      d2 <- str_sub(cumst1$depth[ro], end = 4)
      if (d1 == d2){
          a$total_cells[r] <- cumst1$no_cells[ro]
      }
	  }
    a$p_cells[r] <- (a$Cells[r]/a$total_cells[r])*100
  }
   a$Depth <- as.numeric(a$Depth)

  write.csv(a, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_dis_prob_cells.csv"), row.names = FALSE)
}

merge the u0.4 dataset with the original
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  b <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  c <- rbind(a, b)
  c <- c[!(c$Probability == "0 - 0.09"), ]
  c <- c[!(c$Probability == "0.1 - 0.19"), ]
  c <- c[!(c$Probability == "0.2 - 0.29"), ]
  c <- c[!(c$Probability == "0.3 - 0.39"), ]
  write.csv(c, paste0("../output//maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"))
}
```

ok no try plot

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE)
  head(a)
  d <- unique(a$Depth)
  x <- data.frame(matrix(nrow = length(d)))
  for (s in 1:length(d)){
    dep <- d[s]
    sd <- subset(a, Depth == dep)
    sd <- subset(sd, Probability == "0 - 0.09"| Probability == "0.1 - 0.19"| Probability == "0.2 - 0.29"| Probability == "0.3 - 0.39")
    c <- sum(sd$Cells)
    x$Depth[s] <- dep
    x$Probability[s] <- "0 - 0.39"
    x$cells[s] <- c
    x$p_cells[s] <- 1
  }
  x <- subset(x, select = -c(matrix.nrow...length.d..))
  x$cells[is.na(x$cells)] <- 0
  # for (r in 1:nrow(x)){
  #   d1 <- str_sub(x$Depth[r], end = 4)
  #   for (ro in 1:nrow(cumst1)){
  #     d2 <- str_sub(cumst1$depth[ro], end = 4)
  #     if (d1 == d2){
  #         x$total_cells[r] <- cumst1$no_cells[ro]
  #     }
  #   }
  # }
  # for (r in 1:nrow(x)){
  #    x$p_cells[r] <- (x$Cells[r]/x$total_cells[r])*100

 # }

  write.csv(x, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"))
}
```

merge the u0.4 dataset with the original
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  b <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  c <- rbind(a, b)
  c <- c[!(c$Probability == "0 - 0.09"), ]
  c <- c[!(c$Probability == "0.1 - 0.19"), ]
  c <- c[!(c$Probability == "0.2 - 0.29"), ]
  c <- c[!(c$Probability == "0.3 - 0.39"), ]
  write.csv(c, paste0("../output//maxent/paper_plots/prob_by_depth/", mth, "_u0.4s_dis_prob_cells.csv"))
}
```

@@

ok lets try get an probability for the whole month

```{r}
a <- read.csv("../output/maxent/predictions/jul/dis_prob_cells.csv", header = TRUE)

#subset the probability ranges
p1 <- subset(a, Probability == "0 - 0.09")
p2 <- subset(a, Probability == "0.1 - 0.19")
p3 <- subset(a, Probability == "0.2 - 0.29")
p4 <- subset(a, Probability == "0.3 - 0.39")
p5 <- subset(a, Probability == "0.4 - 0.49")
p6 <- subset(a, Probability == "0.5 - 0.59")
p7 <- subset(a, Probability == "0.6 - 0.69")
p8 <- subset(a, Probability == "0.7 - 0.79")
p9 <- subset(a, Probability == "0.8 - 0.89")
p10 <- subset(a, Probability == ">0.9")

#count the number of cells per probability.

cp1 <- sum(p1$Cells)
cp2 <- sum(p2$Cells)
cp3 <- sum(p3$Cells)
cp4 <- sum(p4$Cells)
cp5 <- sum(p5$Cells)
cp6 <- sum(p6$Cells)
cp7 <- sum(p7$Cells)
cp8 <- sum(p8$Cells)
cp9 <- sum(p9$Cells)
cp10 <- sum(p10$Cells)

tc2 <- sum(cp1, cp2, cp3, cp4, cp5, cp6, cp7, cp8, cp9, cp10) #how many cells in total for novy have a value
tcell <- sum(p1$total_cells) # how many cells are available to have a value...
#tc2 and tcell should match

#create datbase of total cells per probability bin for the month

b <- unique(a$Probability) #get the unique probability bins
c <- as.data.frame(rbind(cp1, cp2,  cp3, cp4, cp5, cp6, cp7, cp8, cp9, cp10))
c$probability <- b
colnames(c) <- c("cells", "prob_bin")
rownames(c) <- c()
c$month <- "jul"
```

make plot of probability over the month
```{r}
pmth <- ggplot(d, aes(month, cells, fill = prob_bin)) + geom_bar(stat='identity') 
plot(pmth)
png(paste0("../output/maxent/predictions/", mthna, "/prob_avg_mth.png"))
print(pmth)
dev.off()
```

merge two months of data together into one file then plot

```{r}
f <- rbind(c, d)
pmth <- ggplot(f, aes(month, cells, fill = prob_bin)) + geom_bar(stat='identity') 
plot(pmth)
png(paste0("../output/maxent/predictions/prob_avg_mth_test.png"))
print(pmth)
dev.off()
```

>>>>

```{r}
mthord <- c("mar") #, "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec"

@@

```{r}
mthord <- c("mar") #,  "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec"
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)

@@

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE)
  head(a)
  d <- unique(cumst1$depth)
  x <- data.frame(matrix(nrow = length(d)))
  for (s in 1:length(d)){
    dep <- d[s]
    sd <- subset(a, Depth == dep)
    sd <- subset(sd, Probability == "0 - 0.09"| Probability == "0.1 - 0.19"| Probability == "0.2 - 0.29"| Probability == "0.3 - 0.39")
    c <- sum(sd$Cells)
    x$Depth[s] <- dep
    x$Probability[s] <- "0 - 0.39"
    x$Cells[s] <- c
    x$p_cells[s] <- 1
    x$total_cells[s] <- 1
  }
  x$Cells[is.na(x$Cells)] <- 0
   for (r in 1:nrow(x)){
     d1 <- str_sub(x$Depth[r], end = 4)
     for (ro in 1:nrow(cumst1)){
       d2 <- str_sub(cumst1$depth[ro], end = 4)
       if (d1 == d2){
           x$total_cells[r] <- cumst1$no_cells[ro]
       }
     }
   }
  for (r in 1:nrow(x)){
    x$p_cells[r] <- (x$Cells[r]/x$total_cells[r])*100
  }
x <- subset(x, select = -c(matrix.nrow...length.d..))
  write.csv(x, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"))
}
```

merge the u0.4 dataset with the original
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  a <- subset(a, select = -c(X))
  b <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  c <- rbind(a, b)
  c <- c[!(c$Probability == "0 - 0.09"), ]
  c <- c[!(c$Probability == "0.1 - 0.19"), ]
  c <- c[!(c$Probability == "0.2 - 0.29"), ]
  c <- c[!(c$Probability == "0.3 - 0.39"), ]
  write.csv(c, paste0("../output//maxent/paper_plots/prob_by_depth/", mth, "_u0.4s_dis_prob_cells.csv"))
}
```

@@

```{r}
probblst <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "_u0.4s_dis_prob_cells.csv", full.names = TRUE)
a <- read.csv(probblst[1])
b <- read.csv(probblst[2])
c <- read.csv(probblst[3])
d <- read.csv(probblst[4])
e <- read.csv(probblst[5])
f <- read.csv(probblst[6])
g <- read.csv(probblst[7])
h <- read.csv(probblst[8])
i <- read.csv(probblst[9])
j <- read.csv(probblst[10])

stackstat <- cbind(a, b[ ,4], c[ ,4], d[ ,4], e[ ,4], f[ ,4], g[ ,4], h[ ,4], i[ ,4], j[ ,4])

colnames(stackstat)

x <- subset(stackstat, select = -c(X, p_cells))
x <- x[ , c(1, 2, 4, 3, 5:13)]
for (r in 1:nrow(x)){
x$totalm[r] <- rowSums(x[r, 4:13])
x$totala[r] <- x$total_cells[r]*10
x$p_cells[r] <- (x$totalm[r]/x$totala[r])*100
}
y <- subset(x, select = c(Depth, Probability, p_cells))
y$Probability <- gsub(">0.9", "0.9 - 1", y$Probability)

probcol <- rev(brewer.pal(7,"RdYlGn"))
bydepth <- ggplot(y, aes(Depth, p_cells, fill = Probability)) + geom_col() + scale_x_reverse() + coord_flip() + scale_fill_manual(values = probcol) 
plot(bydepth)

z <- subset(y, Depth <510)

bydepth <- ggplot(z, aes(Depth, p_cells, fill = Probability)) + geom_bar(stat = "identity") + coord_flip() + scale_x_reverse() + scale_fill_manual(values = probcol) + theme_minimal() #still missing data...
plot(bydepth)

```{r}
z <- subset(y, Depth <510)

bydepth <- ggplot(z, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() + scale_fill_manual(values = probcol) 
plot(bydepth)
```
